%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Developer CV
% LaTeX Template
% Version 1.0 (28/1/19)
%
% This template originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Jan Vorisek (jan@vorisek.me)
% Based on a template by Jan Küster (info@jankuester.com)
% Modified for LaTeX Templates by Vel (vel@LaTeXTemplates.com)
% Modified by Guewen Baconnier
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\pdfminorversion=4

\documentclass[9pt]{developercv} % Default font size, values from 8-12pt are recommended
\usepackage{adjustbox}

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.45\textwidth} % 45% of the page width for name
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% If your name is very short, use just one of the lines below
	% If your name is very long, reduce the font size or make the minipage wider and reduce the others proportionately
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Guewen}}}}} % First name
	
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Baconnier}}}}} % Last name
	
	\vspace{6pt}
	
	{\huge Software Developer / Architect} % Career or current job title
\end{minipage}
\begin{minipage}[t]{0.275\textwidth} % 27.5% of the page width for the first row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{MapMarker}{10}{Chemin des Covets 31,} \\
  % \adjustbox{padding*=22 0 0 0}{1350 Orbe, CH} \\
  \icon{MapMarker}{10}{1350 Orbe, CH} \\
	\icon{Phone}{10}{+41 79 708 24 86}\\
	\icon{At}{10}{\href{mailto:guewen@gmail.com}{guewen@gmail.com}}\\	
\end{minipage}
\begin{minipage}[t]{0.275\textwidth} % 27.5% of the page width for the second row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{Globe}{10}{\href{https://guewen.github.io}{guewen.github.io}}\\
	\icon{Github}{10}{\href{https://github.com/guewen}{github.com/guewen}}\\
	\icon{Twitter}{10}{\href{https://twitter.com/guewenb}{@guewenb}}\\
	\icon{Linkedin}{10}{\href{https://www.linkedin.com/in/guewenb}{linkedin.com/in/guewenb}}\\
\end{minipage}

\vspace{0.5cm}

%----------------------------------------------------------------------------------------
%	INTRODUCTION, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------

\cvsect{Who Am I?}

\begin{minipage}[t]{0.42\textwidth} % 50% of the page width for the introduction text
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
  {A software developer, with an appetite for Open Source, and has learned to
  work in such environment. Creative-minded, curious, eager to learn and
  experiment, I am a key element when it comes to innovate. I have a natural
  ability to understand the big picture and at the same time to focus on
  making the details right. }
\end{minipage}
\hfill % Whitespace between
\begin{minipage}[t]{0.42\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
  {Software Architecture, Development, Business Applications,
    CI, Performance Optimizations, Open Source, Databases,
    Web Services}\\

  \begin{center}
    \bubbles{1/, 2/, 3/, 2/, 1/}
  \end{center}
\end{minipage}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------

\cvsect{Experience}

\begin{entrylist}
	\entry
		{3/2019 -- Now}
		{Software Architect}
		{Camptocamp}
		{Analysis and estimations. Specifications for development tasks. Mentoring.
      Most of my work during this period has been as lead architect and
      developer on a Warehouse Management System \& Supply Chain Application for
      Odoo, allowing to work in large warehouses.
      \\
      \texttt{Python}\slashsep\texttt{JS}\slashsep\texttt{Docker}\slashsep\texttt{PostgreSQL}}
	\entry
		{9/2017 -- 3/2019}
		{Manager of Developers}
		{Camptocamp}
		{Servant leader for developers, coordination and organizations of the teams
      (\textasciitilde{}15 developers). Taking care of recruitment, 1:1 with people and taking
      care of them and the production of the teams. Introduction of improvements
      such as a mentoring system.
      \\
      \texttt{Mentorship}\slashsep\texttt{Communication}\slashsep\texttt{Organization}}
	\entry
		{2015 -- Now}
		{Technical Lead}
		{Camptocamp}
		{Involved in the technical decisions of the department.
      \\ \texttt{Integrity}\slashsep\texttt{Listening}\slashsep\texttt{Big Picture}\slashsep\texttt{Decisiveness}}
	\entry
		{2013 -- Now}
		{OCA Core Maintainer, Contributor, Delegate}
		{Odoo Community Association}
		{Elected as Delegate member of the association, core maintainer.
      Involves an active participation in the projects, including
      reviews, maintenance, support on reported issues, mailing lists. \\
      \texttt{Python}\slashsep\texttt{Odoo}\slashsep\texttt{Community}\slashsep\texttt{Open Source}}
	\entry
		{2010 -- Now}
		{Software Developer}
		{Camptocamp}
		{Implementation of Odoo (Python Open Source ERP) in companies.\\
      Various range of activities, from analysis, development, code reviews, to deployment.
      Highlights (small selection): \\
      Data migration tool in Ruby; Implementation of Odoo for a renowned Swiss
      e-commerce company with custom connector; Mobile application (iOS/Android)
      in Javascript (Ionic/Angular) for Lausanne's Police; Building of an
      internal SaaS platform to deploy Odoo projects with Docker, including CI;
      Performance optimizations with analysis in PostgreSQL/Python;
      Internal tools in Python/JS (Vue.js). \\
      \texttt{Python}\slashsep\texttt{Odoo}\slashsep\texttt{PostgreSQL}\slashsep\texttt{JS}\slashsep\texttt{Ruby}}
	\entry
		{2007 -- 2010}
		{Software Developer \& Architect}
		{SAGE S.A.}
		{Mission at Nespresso on their ERP software. Some achievements:\\
      An advanced rule engine allowing users to compose complex
      marketing rules; SOAP interface in PL/SQL for payment gateways and
      implementation of payments respecting the PCI-SSC rules; SOAP services
      between the e-commerce Shop and the ERP. \\
      \texttt{Oracle DB}\slashsep\texttt{PL/SQL}\slashsep\texttt{Adobe Flex}}
	\entry
		{2006 -- 2007}
		{Software Developer}
		{SAGE S.A.}
		{Delegation missions in private banking. Development of Banking software and
      data migration.\\
      \texttt{Oracle DB}\slashsep\texttt{PLSQL}}
	\entry
		{2002 -- 2003\\\footnotesize{5 months internship}}
		{Web Developer}
		{Omicron Web Services SA}
		{Conception and implementation of an e-commerce shop \\
      \texttt{HTML}\slashsep\texttt{ColdFusion}\slashsep\texttt{JS}\slashsep\texttt{CSS}}
	\entry
		{2002\\\footnotesize{7 months internship}}
		{IT intern}
		{Nestlé Product Technology Center, Orbe}
		{Helpdesk, Web and Software Development \\
      \texttt{ASP}\slashsep\texttt{VB}\slashsep\texttt{HTML}}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	Open Source Projects
%----------------------------------------------------------------------------------------

\cvsect{Open Source Projects}

{A small selection of public projects I initially authored, which now have their
  communities around the world.}\\

\begin{entrylist}
	\entry
		{2013-Now}
		{Odoo Queue Job}
		{\href{https://github.com/oca/queue}{github.com/oca/queue}}
		{A job queue for Odoo. As the time of writing, more than 50
      people have contributed to the project. Used as a basis for many 
      Odoo addons and one of the most used addon worldwide.\\
      \texttt{Odoo}\slashsep\texttt{Python}
    }

	\entry
		{2016-Now}
		{Pytest Odoo}
		{\href{https://github.com/camptocamp/pytest-odoo}{github.com/camptocamp/pytest-odoo}}
		{Pytest is a famous tests runner for Python. Running tests is Odoo is known
      to be slow and tedious. I wrote this extension for pytest which allow to
      run tests selectively and incredibly fast. Reported to me by many devs as
      a lifesaver.\\
      \texttt{Odoo}\slashsep\texttt{Python}
    }
	\entry
		{2017-Now}
		{Odoo Components}
		{\href{https://github.com/OCA/connector/tree/13.0/component}{github.com/oca/connector}}
		{An Odoo addon allowing developers to provide abstract building blocks for
      many usages. Contributors built great and unexpected extensions based on
      this, e.g. for a REST server.\\
      \texttt{Odoo}\slashsep\texttt{Python}
    }
	\entry
		{2013-Now}
		{Odoo Connector}
		{\href{https://odoo-connector.com}{odoo-connector.com}}
		{An Odoo addon that is a powerful framework to build connectors between Odoo
and other platforms. More than 40 contributors joined me on this. Used for many
services that I authored (Magento, Jira) or other contributors authored
(Prestashop, WooCommerce, SFTP, Salesforce, ...).\\
      \texttt{Odoo}\slashsep\texttt{Python}
    }
	\entry
		{2016-Now}
		{Docker Odoo Projects}
		{\href{https://github.com/camptocamp/docker-odoo-project}{github.com/camptocamp/docker-odoo-project}}
		{Base Docker image to run Odoo projects with batteries.\\
      \texttt{Odoo}\slashsep\texttt{Docker}
    }
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\cvsect{Education}

\begin{entrylist}
	\entry
		{2005}
		{Advanced Federal Diploma of Higher Education in Information Technology}
		{CPNV}
		{Web / Software development Option}
	\entry
		{2003}
		{Information Technologist, Federal Diploma of Vocational Education and Training}
		{CPNV}
		{}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	ADDITIONAL INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	\cvsect{Languages}
	
	\textbf{French} - native\\
	\textbf{English} - proficient\\
\end{minipage}
\hfill
\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\cvsect{Besides work}
	
  Time with my family (married, father of two), Music, Bass guitar, Reading, 
  Photography, Walks, Learning new technologies, Board Games, ...
\end{minipage}
\hfill
\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\cvsect{Talks}

  {A Jobs Queue for processing tasks asynchronously}:\\
  {\href{https://guewen.github.io/odoo-2015-connector-queue-job/#1}{guewen.github.io/odoo-2015-connector-queue-job/\#1}}

\end{minipage}

%----------------------------------------------------------------------------------------

\end{document}
